Simulation of Nano Particles in a Laser Trap

### 2017-02-16 doc/draft2.tex
updates

calculated and the measured value can be seen for a representative choice of parameters in Fig.~\ref{fig:measurevscalc}.

>>>>

calculated and the measured value can be seen for a representative choice of parameters in Fig.~\ref{fig:measurevscalc}. There it becomes obvious,
that the measured center of mass temperature rises quicker than the calculated value. This is also the case for different pressures and impinging gas
temperatures. The reason for this may be in the difference of the accomodation factor $\alpha$. In the paper, Millen et al. use an accomodation factor
for a sphere with a value of $\alpha = 0.777$, whereas the accomodation factor for the setup in the simulation for the chosen values is around
$\alpha = 0.016$. This means that the real and the modeled interaction between the gas particles and the nano particle differ from one another.
        \includegraphics[scale=0.3]{images/measurevscalc.pdf}
        \caption{Comparison between the measured (red) and calculated (blue) center of mass temperature according to \cite{MillenJ.2014}.}
        \label{fig:measurevscalc}
